---
title: "p8105_hw1_yy3439"
output: github_document
date: "2023-09-23"
---
## Preperation: Install and Load the package

```{r, echo = FALSE}
library(moderndive) #load the required packages
library(tidyverse)
```



## Problem 1: Load the `early_january_weather` dataset

```{r}
data("early_january_weather")   #load the required dataset

```



## Description

The dataset `early_january_weather` has 15 variables: `origin`, `year`, `month`, `day`, `hour`, `temp`, `dewp`, `humid`, `wind_dir`, `wind_speed`, `wind_gust`, `precip`, `pressure`, `visib`, and `time_hour`. There are 13 numeric variables, 1 character variable, and 1 POSIXct variable. This dataset contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The mean temperature is `r mean(early_january_weather$temp)` .




## Scatterplot


```{r}
ggplot(data = early_january_weather, #create a scatterplot using ggplot
       aes(x = time_hour, y = temp, color = humid)) + geom_point()   #add color 

ggsave("scatter_plot.pdf") #use ggsave() to save the plot in PDF form
```




## Problem 2


```{r}
mydata_df = tibble(        #create a dataframe consisting 
  samp = rnorm(10),        #random sample of size 10 from normal distribution using rnorm function
  vec_logical = samp > 0,  #a logical varible indicating weather each smaple is greater than 0 
  vec_char = c("apple", "sky", "bananna", "blueberries", "sun", "flag", "sea", "shirt", "cherry", "light"),  
                           #a character variable consisting 10 elements
  vec_factor = factor(c("red", "blue","yellow", "blue", "yellow", "red", "blue", "blue", "red", "red"))
                           #a factor variable consisting of 3 levels: red, blue, and yellow
)

```


## Taking the Mean of Each Variable


```{r, eval = FALSE}
samp_mean <- pull(mydata_df, samp) #pull the "samp" column out of the dataframe and take the mean of it 
mean(samp_mean)
vec_logicalmean <- pull(mydata_df, vec_logical) #pull the "vec_logical" column out of the dataframe and take the mean of it 
mean(vec_logicalmean)
vec_charmean <- pull(mydata_df, vec_char) #pull the "vec_char" column out of the dataframe and take the mean of it 
mean(vec_charmean)
vec_factormean <- pull(mydata_df, vec_factor) #pull the "vec_factor" column out of the dataframe and take the mean of it 
mean(vec_factormean)
```

## Discussion on Taking the Mean of Each Variable

Based on the above code chunk and results, we can see that R can calculate the mean value of numerical variables and logical variables. Specifically, when calculating the average of a logical variable, R would treat "TRUE" as 1 and "FALSE" as 0. Therefore, when taking the average of a logical variable, we are actually seeing the proportion of "TRUE" values. However, when trying to take average of the character and factor variables, R gives the result "Warning: argument is not numeric ot logical: returning NA[1] NA. This indicates that R are only able to calculate the average of numerical and logical values by default. Further transformations are required if we are interested in taking the average of character and factor variables. 



##Transform to Numerical Variables


```{r, eval = FALSE}
as.numeric(vec_logicalmean) #translate logical, character, and factor variables to numerical variables
as.numeric(vec_charmean)
as.numeric(vec_factormean)
```

We can see from the output that the `as.numeric` function successfully translated the logical variable to "1" and "0". As a result, it proves that R treats "TRUE" as "1" and "FALSE" as 0. In addition, it assigned the three color levels "1", "2", and "3". However, it fails to translate the character variable to the numeric class, and the error message "Warning: NAs introduced by coercion" was shown. As a result, we should be aware that R might not always translate chracter values to meaningful numerical values. 
