---
title: "p8105_hw1_yy3439"
output: github_document
date: "2023-09-23"
---
## Preperation: Install and Load the package

```{r, echo = FALSE}
library(moderndive)
library(tidyverse)
```



## Problem 1: Load the `early_january_weather` dataset

```{r}
data("early_january_weather")   #load the required dataset

```



## Description

The dataset `early_january_weather` has 15 variables: `origin`, `year`, `month`, `day`, `hour`, `temp`, `dewp`, `humid`, `wind_dir`, `wind_speed`, `wind_gust`, `precip`, `pressure`, `visib`, and `time_hour`. There are 13 numeric variables, 1 character variable, and 1 POSIXct variable. This dataset contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The mean temperature is `r mean(early_january_weather$temp)` .




## Scatterplot


```{r}
ggplot(data = early_january_weather, 
       aes(x = time_hour, y = temp, color = humid)) + geom_point() 
ggsave("scatter_plot.pdf")
```




## Problem 2


```{r}
mydata_df = tibble(
  samp = rnorm(10),
  vec_logical = samp > 0,
  vec_char = c("apple", "sky", "bananna", "blueberries", "sun", "flag", "sea", "shirt", "cherry", "light"),
  vec_factor = factor(c("red", "blue","yellow", "blue", "yellow", "red", "blue", "blue", "red", "red"))
)

```


## Taking the Mean of Each Variable


```{r, eval = FALSE}
samp_mean <- pull(mydata_df, samp)
mean(samp_mean)
ver_logicalmean <- pull(mydata_df, vec_logical)
mean(ver_logicalmean)
ver_charmean <- pull(mydata_df, vec_char)
mean(ver_charmean)
#ver_factormean <- pull(mydata_df, ver_factor)
mean(ver_factormean)
```

## Discussion on Taking the Mean of Each Variable
